---
title: "DSCI_521 Lab 4"
subtitle: "<br/>Question 10"
author: "Markus Nam"
institute: "MDS, UBC"
date: "Sep 29, 2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: inverse

# Making use of Canlang data

--

- Top 5 languages spoken at home from Toronto

--

- Top 10 region with highest % of people claiming Japanese as mother tongue

--

- Top 3 language as mother tongue in Vancouver

---

class: inverse

# Top 5 languages spoken at home from Toronto

--

```{r top 5 spoken at home (Toronto), echo=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
library(canlang)

v_population <- filter(region_data, region == "Toronto") |> pull(population)
v_data <- filter(region_lang, region == "Toronto") |>
 arrange(desc(most_at_home)) |>
 slice(1:5) |>
 mutate(perc_pop = most_at_home / v_population * 100) |>
 select(language, perc_pop)
v_data
```

---

class: inverse

# Top 10 region with highest % of people claiming Japanese as mother tongue

--

```{r top 10 jap as mother tongue, echo=FALSE, message=FALSE}
selected_lang <- region_lang |> 
 filter(language == "Japanese")

selected_lang_pop <- left_join(selected_lang, region_data) |> 
 mutate(mother_tongue_perc = mother_tongue / population * 100) |> 
 select(region, mother_tongue_perc) |> 
 arrange(desc(mother_tongue_perc)) |> 
 slice(1:10)

selected_lang_pop
```

---

class: inverse

# Top 3 languages as mother tongue in Vancouver

--

```{r top 3 mother tongue in Vancouver, echo=FALSE}
population <- filter(region_data, region == "Vancouver") |> select(population) |> pull()
top3 <- region_lang |> filter(region == "Vancouver") |> arrange(desc(mother_tongue)) |> mutate(perc = mother_tongue / population * 100) |> slice(1:3)
barplot(top3$perc, names.arg=top3$language)
```
